### 2015-08-14 writing/SNLI paper/entailment_eval.tex
better EOP model
SICK and RTE results

% The table
\begin{table}
\begin{center}
\def\t#1{\small{#1}}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\toprule
\b{System} & \b{SNLI} & \b{SICK} & \b{RTE-3} \\
\midrule
\t{Edit Distance Based}        & \t{71.9} & \t{65.4} & \b{61.9} \\
\t{Classifier Based}           & \b{72.2} & \b{71.4} & \t{61.5} \\
%\midrule
%\t{Classifier Based (3-class)} & \t{??.?} & \t{65.6} & \t{} \\
%\t{Transformation Based} & \t{36.0} & \t{76.7} & \t{56.4} \\  % broken! At least, on SNLI...
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
2-class test accuracy for two simple baseline systems included in the
  Excitement Open Platform.
%All RTE results are 2-class accuracy.
%The transformation-based model allows for 3-class predictions on our
%  corpus and SICK; these are reported in the last row.
}
\end{table}
%
% END EOP RESULTS TABLE
%

% the best systems
We report results in \reftab{tab:eopresults}, covering both our own test set,
  the SICK test data, and the standard RTE-3 test set \cite{giampiccolo2007third}.
Each of the models was re-trained on the training set of each corpus.
%The results for RTE-3 are taken from \newcite{magnini2014excitement}.
The edit distance and classifier based models are evaluated only on
  2-class entailment; all RTE results are likewise reported for 2-class entailment.
To convert 3-class problems like SICK and SNLI to this setting, all instances
  of \contradiction\ and \unknown\ are converted to nonentailment.
This yields a chance baseline accuracy of 66\% on SNLI, and 71\% on SICK.
This is intended to demonstrate the difficulty of the task, rather than necessarily
  the performance of a state-of-the-art RTE system.
In particular, we omit the models which rely on richer lexical resources or more
  sophisticated algorithms. None of the strongest Excitement Open Platform models
  are designed to scale to large training corpora without modification, and none of them
  succeded at training on the full SNLI training set, with no model showing any measurable    
  progress after several days.

>>>>

% The table
\begin{table}
\begin{center}
\def\t#1{\small{#1}}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\toprule
\b{System} & \b{SNLI} & \b{SICK} & \b{RTE-3} \\
\midrule
\t{Edit Distance Based}            & \t{71.9} & \t{65.4} & \b{61.9} \\
\t{Classifier Based}               & \b{72.2} & \b{71.4} & \t{61.5} \\
\t{Classifier + Lexical Resources} & \b{--}   & \b{78.8} & \t{63.6} \\
%\midrule
%\t{Classifier Based (3-class)} & \t{??.?} & \t{65.6} & \t{} \\
%\t{Transformation Based} & \t{36.0} & \t{76.7} & \t{56.4} \\  % broken! At least, on SNLI...
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
2-class test accuracy for two simple baseline systems included in the
  Excitement Open Platform, as well as SICK and RTE results for
  a model making use of more sophisticated lexical resources.
%All RTE results are 2-class accuracy.
%The transformation-based model allows for 3-class predictions on our
%  corpus and SICK; these are reported in the last row.
}
\end{table}
%
% END EOP RESULTS TABLE
%

% the best systems
We report results in \reftab{tab:eopresults}, covering both our own test set,
  the SICK test data, and the standard RTE-3 test set \cite{giampiccolo2007third}.
Each of the models was re-trained on the training set of each corpus.
%The results for RTE-3 are taken from \newcite{magnini2014excitement}.
The edit distance and classifier based models are evaluated only on
  2-class entailment; all RTE results are likewise reported for 2-class entailment.
To convert 3-class problems like SICK and SNLI to this setting, all instances
  of \contradiction\ and \unknown\ are converted to nonentailment.
This yields a chance baseline accuracy of 66\% on SNLI, and 71\% on SICK.
This is intended to demonstrate the difficulty of the task, rather than necessarily
  the performance of a state-of-the-art RTE system.
In particular, we omit the models which rely on richer lexical resources or more
  sophisticated algorithms. 
None of the strongest Excitement Open Platform models
  are not designed to scale to large training corpora without modification, 
  and none of them succeeded at training on the full SNLI training set, with no 
  model showing any measurable progress after several days.
We include the performance of one such model on the SICK and RTE-3 datasets to
  gauge its relative performance.
